A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-03-12 paper/sections/abstract.tex
Commiting updated sections from JeeHyun and a png version of the core model.

\noindent
{\bf Context}: Since the introduction of the role based access control (RBAC) standard in the late 1990's, 
RBAC has become an increasingly popular access control mechanism for applications such as 
web applications, mobile computing and databases. RBAC restricts access to resources 
based on the identity of subjects connected to logical groupings of permissions called roles.  
The introduction of computing into new domains has led to proposals for extensions to the standard
RBAC model; for example, defining additional constraints among roles, adding context or defining new heirarchy relationships.
\\
\\
\noindent
{\bf Aim}: \textit{The goal of this work is to provide practioners an assessment of the state of extended models of RBAC and researchers with insights into the lack of robust evaluation of RBAC extension models.}
\\
\\
\noindent
{\bf Method}: We conducted a systematic literature review by collecting and synthesizing relevant research
papers in the area of RBAC extensions. We initially collect XXXX papers from sources such as IEEE and ACM 
websites and selected X primary sources.  We performed a comparative analysis of the primary sources to 
find relationships among extended models and analyze the state of RBAC extension evaluations.
\\
\\
\noindent
{\bf Results}:
\\
\\
\noindent
{\bf Conclusions}: We conducted a systematic literature review by collecting and synthesizing relevant research
papers in the area of RBAC extensions. We initially collect XXXX papers from sources such as IEEE and ACM 
websites and selected X primary sources.  We performed a comparative analysis of the primary sources to 
find relationships among extended models and analyze the state of RBAC extension evaluations.

>>>>

\noindent
{\bf Context}: Since the introduction of the role based access control (RBAC) standard in the late 1990's, 
RBAC has become an increasingly popular access control mechanism for applications such as 
web applications, mobile computing and databases. RBAC restricts access to resources 
based on the identity of subjects connected to logical groupings of permissions.  
The introduction of computing into new domains has led to proposals for extensions to the standard
RBAC model; for example, defining additional constraints among roles, adding context or defining new heirarchy relationships.
\\
\\
\noindent
{\bf Aim}: \textit{Researchers looking to expand on the body of knowledge surrounding extensions to RBAC need a starting place to prevent re-invention of the wheel.  
Developers need to find and select an access control mode based on their project requirements. 
The goal of this work is to provide practioners an assessment of the current extensions to RBAC, and researchers with insights into the state of RBAC extension models and how they are evaluated.}
\\
\\
\noindent
{\bf Method}: The authors conducted a systematic literature review by collecting and synthesizing relevant research
papers in the area of RBAC extensions. We initially collected 1716 papers from electronic digital libraries
IEEE, Google Scholar, CiteSeerX and ACM and selected 29 primary sources.  We performed a comparative 
analysis of the primary sources to find relationships among extended models and analyze the state of RBAC extension evaluations.
\\
\\
\noindent
{\bf Results}: Our results showed that extensions to RBAC fall into a number of categorizations that in turn all
fall under the single category of context based extensions.  We look into the motivations behind RBAC extensions and
the domains that are leading factors in developing these newer models. We also quantify the current evaluation methods
used when RBAC extension models are presented to the research community.
\\
\\
\noindent
{\bf Conclusions}:

### 2013-03-12 paper/sections/analysis.tex
Commiting updated sections from JeeHyun and a png version of the core model.

>>>>

Core or any extended role-based access control is used in various aspects of computer systems. In order to reduce efforts for modeling access control used in various applications, researchers often focus on developing generalized core concepts of access control.
We found that propositional logic is used to describe access control model across all categorizations. Propositional logic is concerned with propositions and their logical relationships. In propositional logic, simple (i.e., atomic) or compound condition at given context is evaluated to true or false based on specified rules and access control logic. Researchers are concerned to extend limited set of propositions specific to core RBAC to meet real-world scenarios such as dynamic constraints, temporal, or spatial constraints. However, semantic meanings of such propositions are various based on researchers' intention.

### 2013-03-12 paper/sections/categorization.tex
Adds elimination totals.
Commiting updated sections from JeeHyun and a png version of the core model.

The primary sources contained either within the title, or by multiple references within the body of the text a reference to a quantifier for the
type of extension their model was.  For example, the paper "Privacy-aware role-based access control" \cite{ni2010privacy} contained "privacy" in
the title leading to the papers categorization of Privacy.  By comparison, the paper "An extended RBAC model based on granular logic" \cite{jian2008extended}
does not contain a direct categorization in the title or model name, but in reading the body of the paper the authors assessed that this paper was 
context based.  The authors offer definitions for each categorization and their characteristics based on the primary sources and the english definitions
for each.

@@

  \item Constraint:

  \item Context:

  \item Organizational:

  \item Privacy:

  \item Resource:

@@

  \item Spatio-Temporal:

>>>>

The primary sources contained either within the title, or by multiple references within the body of the text a reference to a quantifier for the
type of extension their model was.  For example, the paper "Privacy-aware role-based access control" \cite{ni2010privacy} contained "privacy" in
the title leading to the papers categorization of Privacy.  By comparison, the paper "An extended RBAC model based on granular logic" \cite{jian2008extended}
does not contain a direct categorization in the title or model name, but in reading the body of the paper the authors assessed that this paper was 
context based.  The authors offer definitions for each categorization and their characteristics based on the primary sources and the English definitions
for each.

@@

  \item Constraint: Access control model in this category extends constraints, which are conditional restrictions on permissions of given roles. This constraint is either static and dynamic. For example, a doctor can modify any medical record for which the doctor is assigned as the designated primary care physician. This example describes doctor's permission with conditional restriction, "only when the doctor is assigned as the designated primary care physician".

  \item Context: Access control model integrates context information. In access control, context often refers to user's current state and environment information (e.g., location, time, system resources, network state, network security configuration, etc) which may affect user's access privileges.

  \item Organizational: Organizational access control is concerned with access control associated with multiple organizations. Typically, users may have the same role name in different organizations, but may have different access privileges due to different local variations.

  \item Privacy: Access control model can be extended to describe privacy policies, which are legal statements or documents about disclose and management of personally identifiable information such as name, address, data of birth, etc.

  \item Resource: Access control model can be extended to handle any system resources (e.g., a file, printer, terminal, database record, etc) in a flexible way.

@@

  \item Spatio-Temporal: Spatio-temporal constraints are combination of spatial (location-based) and temporal (time-based) constraints in specifying access control policies. For example, specific locations are enforced while a role is permitted to conduct an action from 8 am to 5 pm.

### 2013-03-12 paper/sections/core_rbac.tex
Commiting updated sections from JeeHyun and a png version of the core model.

%Each user incorporates a session    
%The user function maps each session to a
%single user, whereas the role function establishes a
%mapping between a session and a set of roles activated
%by the corresponding user in the session.

P1: Describe RBAC entities

P2: Note the 4 levels of RBAC

P3: Concisely describe level 1

P4: Concisely describe level 2

P5: COncisely describe level 3

P6: Concisely describe level 4

>>>>

\begin{figure}[ht]
    \centering
        \includegraphics[width=4.0in]{sections/core-model.png}
    \caption{\label{fig:overview}RBAC Core Diagram in NIST RBAC model \cite{ferraiolokuhn}.}
\end{figure}

Figure~\ref{fig:overview} presents an overview of core RBAC model diagram where elements and their relations are described.
Let "USERS", "ROLES", "OBS", "OPS", "PRM", and "SESSIONS" denote users, roles, objects, operations, permissions, and sessions, respectively.
Permissions are associated with possible users' pre-defined operation on an object (e.g., execute a file).
Note that, at user or role activation, a session associated with user or role is established.
